IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
nit

Simply disallowing all external effects for all browsing contexts is
overly-restricting; pages typically load images, perform XHR requests,
etc.
%
Hence, rather than disallowing all external effects, COWL allows
controlled network communication (inter-frame communication is
dictated by our |send| rule) by associating an implicit label with a
remote host: namely the label corresponding to its origin.
%
In turn, when a task perform a request, the COWL runtime performs the
same label check as that of |send|, e.g., does the task label flow to
the remote origin label.
%
While the external effects of COWL can be formally modeled, and indeed
necessary, we do model these effects in our more general framework,
since, like for Node.js case, this is a platform-specific detail.
%
Indeed, the labeled HTTP client semantics of our Node.js
implementation and that of COWL differ, even though they're both
JavaScript systems, simply because of the different settings.

>>>>

Simply disallowing all external effects for all browsing contexts is
overly-restricting; pages typically load images, perform XHR requests,
etc.
%
Hence, rather than disallowing all external effects, COWL allows
controlled network communication (inter-frame communication is
dictated by our |send| rule) by associating an implicit label with a
remote host: namely the label corresponding to its origin.
%
In turn, when a task perform a request, the COWL runtime performs the
same label check as that of |send|, e.g., does the task label flow to
the remote origin label.
%
While the external effects of COWL can be formally modeled, and indeed
necessary, we do not model these effects in our more general
framework, since, like for Node.js case, this is a platform-specific
detail.
%
Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
though they're both JavaScript systems, simply because of the
different environment.
